Geometric variational problems

### 2020-11-14 NSF2020/Description/specificaim1_ver2.tex
RJR

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing
screening length~\cite{Shibata2004}.
Also, the boundary layers of the solutions to the screen Laplace equation
converge to area measures supported on the particle boundaries
\cite{Lee2018, Lin2015, Shibata2004}.
This phenomena are analogous to the sharp interface limit in the phase-field functional
formulation~\cite{Modica87, MODICA1987487, LuMo89}. PI RR has worked
on phase field approximations of membrane bending
energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
equation~\cite{1531-3492_2006_2_357, Lee2018}.

The following proposed analysis is
a natural outgrowth of prior work because the linearization of the
Poisson-Boltzmann equation is the screened Laplace equations~\eqref{SL}.
We will develop the mathematical connections between the HAP energy and
the energy functionals used in the gradient theory of phase transitions.
%The phase field functional approximates the perimeter of sublevel sets
%of a so-called phase field indicator function. The approximation becomes
%sharp in the zero interfacial thickness limit and minimizers of the
%phase field functional converge (after normalization) to the
%characteristic function of a set solving a perimeter minimization
%problem
~\cite{Modica87, MODICA1987487, LuMo89}. 
One set of questions is to establish the HAP convergence rate as a
function of particle geometry~\cite{LuMo89}, which can be used as a
benchmark for numerical validation.
Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 

>>>>

%  Past researchers expressed the strain tensor in terms of monolayer tangent plane.   
%  In this frame, however, there is a coupling between the gradients of the monolayer surface, lipid direction, and chain length,
%  and accounting for these couplings by Taylor expansion  
%  can lead to an energy density with an unruly number of parameters \cite{PhysRevE.102.042406}.
%
%The form of the elastic energy density \eqref{ansatz3} is the same as
%  the Oseen-Frank energy density for nematic liquid crystals \cite{ANDRIENKO2018520,Tran7106,Helfrich73}.   In fact,  
%  a lipid monolayer acts as one layer in a smectic  phase \cite{REYESMATEO1995978,Rangamani20140463,PhysRevLett.113.248102}. 
%  Motivated by liquid crystal theory, we have found that the gradient terms completely decouples when 
%  expanding the strain tensor, not in terms of the monolayer tangent plane, but in terms of a plane perpendicular to ${\bf n}$. 
%  Using this observation, we prove an exact identity 
%  that gives the incompressibility condition by a Steiner-type polynomial in $\Div {\bf n}$ and $\det \nabla {\bf n}$ \cite{Fe59}.
%  In contrast, the works \cite{TerziDeserno17, PhysRevE.102.042406, Hamm2000, C9SM02079A} utilize an
%  approximate identity for incompressibility, and so we can offer a considerably more accurate analysis of monolayer energy.
%  
%%To measure the twist modulus, we place a single monolayer on a hydrophobic substrate 
%%and take the initial configuration ${\bf n} = (0, f(x_1), \sqrt{1 - f^2(x_1)})$,
%%yielding a surface gradient $\nabla {\bf n} = \begin{pmatrix}0 & 0\\ f'(x_1) & 0\end{pmatrix}$. 
%%  Here $\Div {\bf n} = \mathrm{tr}(\nabla {\bf n}) = 0$, $\det(\nabla {\bf n}) = 0$ and
%%  $\Curl {\bf n} = (\nabla u)_{12} - (\nabla u)_{21} = f'(x_1)$.
%%  This gives the continuum elastic energy equals
%%  \begin{equation}
%%    \label{eq:twist_energy}
%%    E = \int_{\Sigma} \tfrac{1}{2}\KT (f'(x_1))^2 + \tfrac{1}{2} \KTH f^2(x_1) \,\dif dx_1 \dif x_2,
%%  \end{equation}
%%  which we compare to the HAP simulation data.
%
\subsubsection{Asymptotic analysis on the limit $\rho\rightarrow 0$ of HAP}
The HAP energy converges to the surface energy in the limit of vanishing screening length~\cite{Shibata2004}.
Also, the boundary layers of the solutions to the screen Laplace equation
converge to area measures supported on the particle boundaries \cite{Lee2018, Lin2015, Shibata2004}.
These phenomena are analogous to the sharp interface limit in the phase-field functional,
and motivate developing the mathematical connections between the HAP energy and
the energy functionals used in the gradient theory of phase transitions.
formulation~\cite{Modica87, MODICA1987487, LuMo89}.
PI RR has worked on phase field approximations of membrane bending
energy~\cite{0951-7715-18-3-016} and asymptotcs in the Poisson-Boltzman
equation~\cite{1531-3492_2006_2_357, Lee2018}.
The screened-Laplace equations~\eqref{SL} is the linearization of the Poisson-Boltzmann equation.
One set of questions is to establish the HAP convergence rate as a
function of particle geometry~\cite{LuMo89}, which can be used as a
benchmark for numerical validation.
Ultimately, we will be able to address the so-called $\Gamma$-convergence of energy minimizing
particle configurations in the zero-decay length limit \cite{Roger2006, Mugnai2013}. 
%The phase field functional approximates the perimeter of sublevel sets
%of a so-called phase field indicator function. The approximation becomes
%sharp in the zero interfacial thickness limit and minimizers of the
%phase field functional converge (after normalization) to the
%characteristic function of a set solving a perimeter minimization
%problem
%
%
